---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sacRebleu

<!-- badges: start -->
<!-- badges: end -->

The goal of sacRebleu is to provide a simple interface to the BLEU score, a metric for evaluating the quality of generated text.
This package is inspired by the NLTK and sacrebleu implementations of the BLEU score, and is implemented in C++ for the R programming language.

## Installation

You can install the development version of sacRebleu from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("LazerLambda/sacRebleu")
```

## Example

```{r example}
library(sacRebleu)
cand_corpus <- list("This is good", "This is not good")
ref_corpus <- list(list("Perfect outcome!", "Excellent!"), list("Not sufficient.", "Horrible."))
bleu_corpus <- bleu_corpus(ref_corpus, cand_corpus)
```

